Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
More citations

@@

\subsubsection{CMU Sphinx}

CITATION FOR AARON \cite{CMU:Sphinx}.

>>>>

As mentioned in section \ref{sec:related}, many other applications failed to create a captivating game for children. We wanted to have an application that children would see less as homework, and more of a game. This was the underlying motivation for making {\em Kimbee} a game. In order for a game to be immersive, a sense of progression must be present \cite{Ermi:Gameplay}.

@@

\subsubsection{CMU Sphinx}
CMU Sphinx\cite{CMU:Sphinx} is a speech processing library. There is a JavaScript port that allows audio recognition in the browser. Our {\em Speech Processing} component utilizes this JavaScript port to do audio recognition in the browser without server assistance. To deduce correct child speech we utilize this library creating target word and invalid word pairs. For example, when targeting `R' sounds, we can use CMU Sphinx to recognize the target word `Rabbit' or a invalid word `Wabbit.' With a large dictionary of words this has been effective in distinguishing replacements caused by speech disorders.

\subsubsection{Server Application Programming Interface}
The {\em Server Application Programming Interface} is what connects the Kimbee system to our central recording server. Once audio is processed by the {\em Speech Processing}, it is sent off via POST request in raw microphone form to the central server if a internet connection is present. A unique identifier is computed and stored by the Kimbee System that will uniquely identify recordings in the central server as belonging to a particular child's device. This unique identifier is accessible via the Options Screen in the {\em Phaser Game Implementation}.
